%-------------------------
% Resume - Boshen Lin
% Optimized for 2025/2026 Canadian CS New Grad Market
% Key changes: Skills moved up (ATS), publication elevated,
% bullets tightened with XYZ impact, keyword density improved,
% AI/ML emphasis, consolidated to strict 1-page
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tight margins
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1.00in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.30in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Machine-readable PDF
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        #1 \vspace{-2pt}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
            \textit{\small #3} & \textit{\small #4} \\
        \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \small #1 & #2 \\
        \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Boshen Lin} \\ \vspace{2pt}
    \small (825) 983-2210 $|$
    \href{mailto:blin1@ualberta.ca}{blin1@ualberta.ca} $|$
    \href{https://blin2k.github.io}{blin2k.github.io} $|$
    \href{https://github.com/blin2k}{github.com/blin2k} $|$
    \href{https://www.linkedin.com/in/boshen-lin/}{linkedin.com/in/boshen-lin}
\end{center}

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {University of Alberta}{Edmonton, AB}
            {Bachelor of Science in Computing Science (Honors)}{Sept. 2021 -- May 2026}
            \resumeItemListStart
                \resumeItem{\textbf{First-Author Publication} at CSCE 2025 $|$ \textbf{Coursework:} Compilers, OS, Algorithms, ML, Deep Learning, Databases, Software Engineering}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS (moved up for ATS scanning)----------- 
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
            \textbf{Languages:} Python, TypeScript, JavaScript, Kotlin, C++, Java, Go, Rust, SQL, HTML/CSS \\
            \textbf{Frameworks:} React, Vue 3, Next.js, tRPC, GraphQL, Django, Express, Spring Boot, Android SDK, PyTorch \\
            \textbf{Cloud \& DevOps:} Amazon Web Services (AWS S3, EC2), Docker, GitHub Actions CI/CD, Firebase, Google Cloud \\
            \textbf{Data \& Tools:} PostgreSQL, MongoDB, Redis, REST APIs, Git, Linux, Agile/Scrum, Jira, pytest, Playwright
        }}
    \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart

        \resumeSubheading
            {Software Engineer}{Oct. 2025 -- Present}
            {University of Alberta -- Civil \& Environmental Engineering}{Edmonton, AB}
            \resumeItemListStart
                \resumeItem{Designed and built modular Android app with event-driven architecture, streaming 5-channel biosignal data via UDP/TCP at 50--200 Hz; engineered Kotlin rendering pipeline with unit tests achieving sub-100ms latency and 99.2\% signal fidelity.}
            \resumeItemListEnd

        \resumeSubheading
            {Full-Stack Software Engineer Intern}{Dec. 2024 -- Oct. 2025}
            {So Shall We.co}{Edmonton, AB}
            \resumeItemListStart
                \resumeItem{Built full-stack analytics platform with microservices architecture (React, TypeScript, Node.js) aggregating 500K+ daily metrics from Google Ads, Meta Ads, and GA4 APIs, reducing manual reporting by 85\%.}
                \resumeItem{Designed automated ETL pipeline with data validation and AWS S3 storage handling 2GB+ daily ingestion with partitioning.}
                \resumeItem{Containerized services with Docker; deployed CI/CD via GitHub Actions with automated testing and PR review workflows; tracked sprints in Jira; achieved 99.5\% pipeline reliability.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{May 2024 -- Sept. 2024}
            {University of Alberta -- Civil \& Environmental Engineering}{Edmonton, AB}
            \resumeItemListStart
                \resumeItem{Designed and deployed Android app processing 10,000+ real-time sensor data points with HRV analysis pipeline and KDE heatmap visualization on Google Maps; 92\% accuracy across 50+ users.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer Intern}{May 2023 -- Sept. 2023}
            {Leettle Mint LLC}{Pittsburgh, PA}
            \resumeItemListStart
                \resumeItem{Developed Vue 3 SPA with component-level unit tests and real-time financial data visualization serving 1,000+ daily active users.}
                \resumeItem{Optimized MongoDB queries via compound indexing and Redis caching layer, reducing API latency by 50\% while supporting 100+ concurrent connections with pagination and rate limiting.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Gazprea Compiler} $|$ \emph{C++, ANTLR, MLIR}}{} 
            \resumeItemListStart
                \resumeItem{Built complete compiler toolchain (lexer, parser, semantic analyzer, MLIR codegen) for a custom language with 50+ grammar rules, type inference, scoped symbol tables, and optimized SSA-form IR generation.}
            \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{Generative Models Benchmark Suite} $|$ \emph{Python, PyTorch, CUDA}}{} 
            \resumeItemListStart
                \resumeItem{Implemented VAE, DDPM, DDIM, and Latent Diffusion from scratch in PyTorch; achieved 2.3x training speedup via mixed precision (AMP) and cosine scheduling; benchmarked with FID/SSIM/MSE across 100+ Weights \& Biases runs.}
            \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{Crane Path Optimization} $|$ \emph{Python, NumPy, SciPy}}{} 
            \resumeItemListStart
                \resumeItem{Developed multi-objective optimization algorithm reducing search complexity by 97\% through spherical coordinate transformation; validated on 5 real construction site layouts with collision-free paths.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------AWARDS & LANGUAGES-----------
\section{Awards \& Languages}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
            \textbf{Awards:} International Student Scholarship (2021--2023), UAlberta Undergraduate Leadership Award (2023) $|$ \textbf{Languages:} English, Cantonese (Native), Mandarin (Native)
        }}
    \end{itemize}

%-------------------------------------------
\end{document}
